Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review

### 2023-06-25 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Used the right dataset name

## Breakdown of studies before and after 2005
```{r}
before_2005 <- data_without_fmd %>% 
  select(publication_year) %>% 
  mutate(before_2005 = ifelse(publication_year <= 2005, "yes", "no")) %>% 
  count(before_2005) %>% 
  adorn_percentages(denominator = 'col') %>% 
  adorn_pct_formatting() %>% 
  adorn_ns(position = "front")

@@

## Publications per year
```{r}
publications_per_year <- data_without_fmd %>%
  count(publication_year)

>>>>

## Breakdown of studies before and after 2005
```{r}
before_2005 <- compact_data_with_citation_keys_no_fmd %>% 
  select(publication_year) %>% 
  mutate(before_2005 = ifelse(publication_year <= 2005, "yes", "no")) %>% 
  count(before_2005) %>% 
  adorn_percentages(denominator = 'col') %>% 
  adorn_pct_formatting() %>% 
  adorn_ns(position = "front")

@@

## Publications per year
```{r}
publications_per_year <- compact_data_with_citation_keys_no_fmd %>%
  count(publication_year)
